% LaTeX file for resume
% This file uses the resume document class (res.cls)
\documentclass{res}
\include{private}

\name{\Huge{Celia Siu}\\[4pt]}
\address{%
  \centerline{%
    \faEnvelopeO{ \email }%
    \faMobile{ \cellphone }}\\%
    \centerline{ \where $|$ \url{csiu.github.io} }\\
  \rule{\textwidth}{0.4pt}{}}


% Customize spacing
\newsectionwidth{0pt}  % So the text is not indented under section headings
\topmargin=-0.5in      % start text higher on the page

% Customize the header
\usepackage{fancyhdr}
\pagestyle{fancy}                  % set pagestyle for document
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
% - Adjust spacing
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}    % space between header and text
\setlength{\footskip}{0pt}
% - Define headers and footers
\rhead{}% {\it csiu}\\{\it p. \thepage} }
\cfoot{%
  \rule{\textwidth}{0.4pt}{}
  \faLinkedinSquare{ \url{https://ca.linkedin.com/in/celiasiu} }
  \faGithub{ \url{http://github.com/csiu} }\\
  \faStackOverflow{ \url{http://stackoverflow.com/users/2364901/csiu} }\\
  % \faTwitter{ \url{https://twitter.com/celiassiu} }
}

% Enable use of packages
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{fontawesome}

% Enable link
\usepackage{hyperref}

% Enable condition ifthenelse
\usepackage{ifthen}

% Enable spacing
\usepackage{scrextend}

% ------------------------------------------------------------------------------
% Customizations - pt.2

% - Update section header
\renewcommand{\section}[1]{%
  \vspace{0.3in}%
  \centerline{\uppercase{\bf{#1}}}%
  \vspace{-6pt}}

% - Award line
\newcommand{\lineaward}[2]{%
  #1 \faTrophy{} #2\\[1ex]}

% - Presentation lines
\newcommand{\linepresentation}[3]{%
  #3 \hfill #1\\[.75ex]}

% - Employment header lines
\newcommand{\linehead}[2]{%
  {\bf #1} \hfill #2\\}
\newcommand{\linetitle}[1]{%
  {\sl #1}}

% - Volunteer line
\newcommand{\linevolunteer}[3]{%
  {\sl #3}, {\bf #2} \hfill #1}%\\[.5ex]}

% - define new environment for publications
\newenvironment{publicationlists}{%
  \begin{itemize}\leftmargin=3em \itemindent=-1em \itemsep=2pt%
  }{%
  \end{itemize}}

% - Define achievement & awards section
\newcommand{\awarditem}[3]{%
  \ifthenelse{\equal{#2}{}}
    {{\bf #1}}
    {{\bf #1}\hfill#2}
    \\ \vspace{-1em}
    \begin{addmargin}[2em]{3em}% 2em left, 3em right
    #3
    \end{addmargin}
    \vspace{-1em}
    }

% - update itemize have smaller itemsep
\let\olditemize\itemize
\renewcommand{\itemize}{%
  \olditemize\addtolength{\itemsep}{-4pt}}

% - url to roman (serif) font
\urlstyle{rm}


% ==============================================================================
\begin{document}
\begin{resume}

% \thispagestyle{empty} % no header on first page

% ------------------------------------------------------------------------------
\vspace{-1em}
\begin{center}
  {\it A highly practical and organized BI Consultant with technical abilities, 4yrs of industry and 4yrs of academia experience. I value efficiency, autonomy and am interested in simplification, automation, and innovation.}
\end{center}
\vspace{-1.5em}

\section{Work Experience}

{\bf Business Intelligence Consultant II} \hfill Aug 2020 -- Present\\
{\it Visier Inc.}
\begin{itemize}
  \item Guided data discovery consultation meetings with customers to educate, explore options, and gather requirements for delivering value on their business use cases
  \item Created internal and customer-facing assets including best practice documentations in Confluence and ServiceNow
\end{itemize}

{\bf Sr. Data Management Engineer, Lead} \hfill Jul 2019 -- Aug 2020\\
{\it Visier Inc.}
\begin{itemize}
  \item Reviewed new customer onboarding activities and business logic customizations by assessing requirements, evaluating technical implementation design proposals, and doing code reviews
  \item Followed the Scrum agile framework for managing sprint planning in JIRA and leading sprint review and retrospective meetings
\end{itemize}

{\bf Data Management Engineer II, Lead} \hfill Jul 2018 -- Jul 2019\\
{\it Visier Inc.}
\begin{itemize}
  \item Coached, mentored, and trained up junior and new staff
  \item Gave presentations to small and large groups during training sessions, workshops, team all hands meetings, and new hire info sessions
\end{itemize}

{\bf Data Management Engineer I} \hfill May 2017 -- Jul 2018\\
{\it Visier Inc.}
\begin{itemize}
  \item Extracted, transformed, and loaded large amounts of customer HR data into the Visier application using Mercurial/Git and proprietary DSL
\end{itemize}

{\bf Bioinformatics Research Assistant} \hfill Sept 2013 -- Aug 2014\\
{\it BC Cancer Agency, Shah Lab}
\begin{itemize}
  \item Preprocessed data, developed pipelines, and wrapped third party software using R, Python and Bash
  \item Produced data visualizations and limited text suitable for scientific manuscripts with R (eg. ggplot2)
  \item Initiated pipelines on compute clusters to generate data for downstream analysis in Python and Bash
\end{itemize}

% \vspace{-1em}
% \section{Projects}
%
% \linehead{100 Days of Code}{Feb 2017 -- Jun 2017}
% \linetitle{See my technical blog: \url{http://csiu.github.io/blog/tag/100daysofcode}}
% \begin{itemize}
%   \item Formulated models using machine learning methods from Scikit-learn to enter Kaggle competitions
%   \item Setup and used PostgreSQL databases to gain experience with SQL and learn new technologies
%   \item Analyzed data using Python (eg. Pandas, Matplotlib, BeautifulSoup, Nltk, Theano), R, D3, \& APIs
% \end{itemize}

% \vspace{-1em}
% \section{Volunteer experience}
% \linevolunteer{Oct 2016 \& Feb 2017}{%
%   Software Carpentry workshop}{%
%   Volunteer}
% \begin{itemize}
%   \item Troubleshot and helped students learn Git, GitHub, Bash, Python, and Jupyter Notebook
% \end{itemize}

\vspace{-1em}
\section{Education}
{\bf Master of Science, Bioinformatics $|$ UBC, Vancouver}\hfill{Sept 2014 -- May 2017}
\begin{itemize}
  \item 10\% acceptance rate and awarded \$50,000+ in scholarships and travel grants
  \item 7 publications in the general field of Bioinformatics
  \item Graduate-level coursework in Machine Learning, Data Mining, and Design and Analysis of Algorithms
  \item MSc Thesis: {\it Characterization of the human thyroid epigenome.}
  In characterizing and modelling thyroid epigenetic data, I developed a novel metric for model selection (available as an R package "hmmpickr" on my Github) and built a data analysis pipeline.
\end{itemize}

\pagebreak

\end{resume}
\end{document}
